\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T5]{fontenc}
\usepackage{geometry}
\geometry{a4paper, margin=0.75in}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{tabularx}

% Colors
\definecolor{primaryColor}{RGB}{33, 50, 94}
\definecolor{secondaryColor}{RGB}{62, 73, 122}

% Links and PDF metadata
\hypersetup{
    colorlinks=true,
    urlcolor=primaryColor,
    pdftitle={Nguyen Van Tien Phat - Cybersecurity Resume},
    pdfauthor={Nguyen Van Tien Phat},
    pdfsubject={SOC Analyst and Cybersecurity Resume},
    pdfkeywords={SOC Analyst, Cybersecurity, SIEM, SOAR, Wazuh, Kaspersky KUMA}
}

% Section formatting
\titleformat{\section}{\Large\bfseries\color{primaryColor}}{}{0em}{}[\color{primaryColor}\titlerule]
\titlespacing*{\section}{0pt}{1.05ex plus .5ex minus .2ex}{.65ex plus .2ex}
\setlist[itemize]{itemsep=1pt, topsep=1pt, parsep=0pt, partopsep=0pt}

% Resume helpers
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabularx}{\linewidth}[t]{@{}Xr@{}}
      \textbf{#1} & \textbf{#2} \\
      \textit{#3} & \textit{#4} \\
    \end{tabularx}\vspace{-1pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-1pt}\item
    \begin{tabularx}{\linewidth}[t]{@{}Xr@{}}
      \textbf{#1} & \textbf{#2} \\
    \end{tabularx}\vspace{-1pt}
}

\pagestyle{empty}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{\color{primaryColor} Nguyen Van Tien Phat}} \\ \vspace{8pt}
    \small \faPhone\ 0976 459 403 \quad
    \faEnvelope\ \href{mailto:nguyenphat0976459403@gmail.com}{nguyenphat0976459403@gmail.com} \\ \vspace{3pt}
    \faGlobe\ \href{https://tienphat.tech}{tienphat.tech} \quad
    \faMapMarker\ Ho Chi Minh City, Vietnam
\end{center}

% Professional summary
\section*{PROFESSIONAL SUMMARY}
Cybersecurity student pursuing a career in security operations, with hands-on experience configuring network and monitoring infrastructure, analyzing security logs, and automating incident response workflows. Experienced with Kaspersky KUMA, Wazuh, Suricata, pfSense, and n8n. Seeking a SOC Intern or Security Analyst role to strengthen detection engineering skills and contribute to enterprise security operations.

% Education
\section*{EDUCATION}
\begin{itemize}[leftmargin=0.15in, label={}]
  \resumeSubheading
    {Ho Chi Minh City University of Foreign Languages and Information Technology (HUFLIT)}{09/2023 - 05/2026}
    {Cybersecurity, Faculty of Information Technology}{Ho Chi Minh City, Vietnam}
\end{itemize}

% Work experience
\section*{WORK EXPERIENCE}
\begin{itemize}[leftmargin=0.15in, label={}]
  \resumeSubheading
    {Confidential Technology Company}{01/2026 - 05/2026}
    {SOC Intern}{Ho Chi Minh City, Vietnam}
    \begin{itemize}[leftmargin=0.15in, label=\textbullet]
        \item Deployed and configured Kaspersky KUMA SIEM to monitor Apache and Nginx web server logs; developed correlation rules to detect DDoS activity, web scanning, and website defacement.
        \item Built attack-scenario proofs of concept and corresponding monitoring use cases to validate SOC infrastructure and detection coverage.
        \item Authored incident response playbooks and swimlane workflows aligned with NIST SP 800-61 Rev. 2.
    \end{itemize}
\end{itemize}

% Projects
\section*{SELECTED PROJECTS}
\begin{itemize}[leftmargin=0.15in, label={}]
  \resumeProjectHeading
    {SDN Centralized Log Collection System}{03/2026 - 05/2026}
    \begin{itemize}[leftmargin=0.15in, label=\textbullet]
        \item Built a software-defined networking lab with \textbf{Mininet} and the \textbf{Ryu Controller}.
        \item Developed a centralized log ingestion pipeline for virtual switches and routers, providing consistent visibility across the SDN environment.
        \item \textbf{Outcome:} Improved traffic monitoring and enabled earlier detection of anomalous behavior across the SDN infrastructure.
    \end{itemize}
  \vspace{2pt}
  \resumeProjectHeading
    {Enterprise SOC Monitoring \& SOAR System}{10/2025 - 11/2025}
    \begin{itemize}[leftmargin=0.15in, label=\textbullet]
        \item Segmented the network with VLANs on \textbf{pfSense} and implemented \textbf{WPA2-Enterprise} authentication with FreeRADIUS.
        \item Deployed \textbf{Suricata} in inline mode to detect and automatically block DDoS activity and Nmap scans.
        \item Created \textbf{Wazuh SIEM} rules for centralized monitoring and detection of rogue DHCP and SSH brute-force activity.
        \item Automated incident response with \textbf{n8n}, including risk scoring, Telegram alerts, and malicious IP blocking on the firewall.
        \item Developed a real-time security monitoring dashboard with \textbf{ReactJS} and \textbf{Supabase}.
        \item \textbf{Outcome:} Delivered a closed-loop SOC prototype that detected and blocked simulated attacks within seconds.
    \end{itemize}
\end{itemize}

% Technical skills
\section*{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Security Monitoring \& SOC Operations:} SIEM (Wazuh, KUMA), log analysis (Sysmon, Windows Event Logs, Syslog), IOC identification, and security alert configuration.
    \item \textbf{Security Tools \& Automation:} Firewalls and routing (pfSense, iptables), IDS/IPS (Suricata), network authentication (FreeRADIUS), SOAR and integration (n8n), Docker, and Docker Compose.
    \item \textbf{Systems \& Networking:} Windows Server (Active Directory, DNS, DHCP, GPO), basic Linux administration, OSI model, and TCP/IP fundamentals.
    \item \textbf{Programming \& Databases:} C\#, Java, JavaScript, Python, and Supabase.
\end{itemize}

% Languages
\section*{LANGUAGES}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{English:} Intermediate proficiency; comfortable reading technical documentation.
\end{itemize}

\end{document}
